Modelling BCG vaccination in the UK

### 2019-12-10 rmds/01-introduction.Rmd
reference corrrections

Mechanistic mathematical models provide an assumption based framework for understanding the transmission of infectious diseases.[@Anderson1991] Mechanistic models can be used to simplify complex real-world systems, whilst retaining a linkage to real-world processes.[@Keeling2007] They are unlike statistical models, which instead focus on modelling the underlying structure of the data generally without reference to the real-world processes. There are multiple mechanistic modelling approaches, the most common being compartmental based models and individual based models.[@Anderson1991; @Keeling2007] Both of these approaches can be represented as  deterministic, semi-stochastic, or fully stochastic - both of the latter include a random component whilst the former does not. Recently, mechanistic models have been combined with statistical models to account for the fact that events may be only partially observed.[@King] Mechanistic models have an advantage over statistical models in that they can more easily be used to compare alternative scenarios over long periods of time for which observed data does not exist.

>>>>

Mechanistic mathematical models provide an assumption based framework for understanding the transmission of infectious diseases.[@Anderson1991] Mechanistic models can be used to simplify complex real-world systems, whilst retaining a linkage to real-world processes.[@Keeling2007] They are unlike statistical models, which instead focus on modelling the underlying structure of the data generally without reference to the real-world processes. There are multiple mechanistic modelling approaches, the most common being compartmental based models and individual based models.[@Anderson1991; @Keeling2007] Both of these approaches can be represented as  deterministic, semi-stochastic, or fully stochastic - both of the latter include a random component whilst the former does not. Recently, mechanistic models have been combined with statistical models to account for the fact that events may be only partially observed.[@King2016] Mechanistic models have an advantage over statistical models in that they can more easily be used to compare alternative scenarios over long periods of time for which observed data does not exist.

### 2019-12-10 rmds/04-tb-epi-england.Rmd
reference corrrections

Age-standardised rates were calculated using the `r 'epiR'` package for R,[@Stevenson2016] using the average age distribution of England from 2000-2015 as the standard population to allow comparison between years. Those aged 90+ were excluded as demographic data for this population were unreliable. The code used to calculate incidence rates is available online as an R package (`tbinenglanddataclean`^[`tbinenglanddataclean`: https://github.com/seabbs/tbinenglanddataclean]; see Chapter \@ref(introduction)).

>>>>

Age-standardised rates were calculated using the `r 'epiR'` package for R,[@EpiR] using the average age distribution of England from 2000-2015 as the standard population to allow comparison between years. Those aged 90+ were excluded as demographic data for this population were unreliable. The code used to calculate incidence rates is available online as an R package (`tbinenglanddataclean`^[`tbinenglanddataclean`: https://github.com/seabbs/tbinenglanddataclean]; see Chapter \@ref(introduction)).

### 2019-12-10 rmds/06-tb-bcg-improv-outcomes.Rmd
reference corrrections

I conducted sensitivity analyses to assess the robustness of the results, by dropping each confounding variable in turn and assessing the effect on the adjusted Odds Ratios (aORs) of the exposure variable. I repeated the analysis excluding duplicate recurrent cases, and restricting the study population to those eligible for the BCG schools scheme (defined as UK born cases that were aged 14 or over in 2004) to assess the comparability of the BCG vaccinated and unvaccinated populations. To mitigate the impact of missing data I used multiple imputation, with the MICE package.[@VanBuuren2011] I imputed 50 data sets (for 20 iterations) using all outcome and explanatory variables included in the analysis as predictors along with Public Health England centre. The model results were pooled using the small sample method,[@Barnard1999] and effect sizes compared with those from the main analysis. All code for this analysis is available online^[Code: https://github.com/seabbs/ExploreBCGOnOutcomes].

>>>>

I conducted sensitivity analyses to assess the robustness of the results, by dropping each confounding variable in turn and assessing the effect on the adjusted Odds Ratios (aORs) of the exposure variable. I repeated the analysis excluding duplicate recurrent cases, and restricting the study population to those eligible for the BCG schools scheme (defined as UK born cases that were aged 14 or over in 2004) to assess the comparability of the BCG vaccinated and unvaccinated populations. To mitigate the impact of missing data I used multiple imputation, with the MICE package.[@Groothuis-oudshoorn] I imputed 50 data sets (for 20 iterations) using all outcome and explanatory variables included in the analysis as predictors along with Public Health England centre. The model results were pooled using the small sample method,[@Barnard1999] and effect sizes compared with those from the main analysis. All code for this analysis is available online^[Code: https://github.com/seabbs/ExploreBCGOnOutcomes].
